TBD

### 2021-02-26 outputs/paper/paper.Rmd
Edit captions

```{r Q7, echo = FALSE, message = FALSE}
### Between Oct 1 and Dec 31 was your total sales revenue higher, lower, or about the same as it was during the previous quarter (last quarter dates)? *
### Higher
### Lower
### Around the Same
ggplot(data = all_simulated_dataset, mapping = aes(x = Q7, fill = type)) + 
  geom_bar() +
  labs(x = "Revenue Change",
       y = "# of Restaurants",
       title = "Revenue changes between Oct 1 and Dec 31",
       fill = "Condition") +
  theme_fivethirtyeight() + 
  scale_fill_tableau(labels = c("Control", "Intervention"), guide = guide_legend(reverse = TRUE))

### Chi-squared test
q7_chi <- table(all_simulated_dataset$Q7, all_simulated_dataset$type) %>%
  chisq.test()
tableChisq("Pearson's Chi-squared test to examine the possibility of an association between the intervention and the total sales", q7_chi$statistic, q7_chi$parameter, q7_chi$p.value)
```

```{r Q8, echo = FALSE, message = FALSE}
### What was the approximate percentage decrease in total sales revenue between Oct 1 and Dec 31 compared to the during the previous quarter (last quarter dates)? *
### Decline of 50% or more
### Decline of 25% to 50%
### Decline of 10% to 25%
### Decline of 10% or less
ggplot(data = all_simulated_dataset, mapping = aes (x = Q8, fill = type)) +
  geom_bar(position = "stack") + coord_flip() +
  scale_x_discrete(limit = c("Decline of 50% or more", "Decline of 25% to 50%", "Decline of 10% to 25%", "Decline of 10% or less")) + 
  labs(x = "Aprrox. % Decrease in Total Sales Revenue",
       y = "# of Restaurants",
       title = str_wrap("Percentage of total sales revenue decrease between Oct 1 and Dec 31", 40),
       fill = "Condition") +
  theme_fivethirtyeight() + 
  scale_fill_tableau(labels = c("Control", "Intervention"), guide = guide_legend(reverse = TRUE))

### Chi-squared test
q8_chi <- table(all_simulated_dataset$Q8, all_simulated_dataset$type) %>%
  chisq.test()
tableChisq("Pearson's Chi-squared test to examine the relation between the intervention and the total sales and a decline in revenue", q8_chi$statistic, q8_chi$parameter, q8_chi$p.value)
```

```{r Q9, echo = FALSE, message = FALSE}
### Before Oct 1st, approximately how much of your total monthly sales revenue came from takeout or delivery? *
### Did not offer takeout or delivery
### 25% or less
### 25- 50%
### 50-75%
### 75% or more

my_title = "Total revenue from takeout/delivery prior to Oct 1"
ggplot(data = all_simulated_dataset, mapping = aes (x = Q9, fill = type)) +
  geom_bar(position = "stack") +  coord_flip() + 
  scale_x_discrete(limit = c("Did not offer takeout or delivery", "25% or less", "25-50%", "50-75%", "75% or more")) + 
  labs(x = "Total Monthly Sales Revenue Fromt Takeout or Delivery",
       y = "# of Restaurants",
       title = str_wrap("Total revenue from takeout or delivery prior to Oct 1", 30),
       fill = "Condition") +
  theme_fivethirtyeight() + 
  scale_fill_tableau(labels = c("Control", "Intervention"), guide = guide_legend(reverse = TRUE))
```

@@

```{r Q11, echo = FALSE, message = FALSE}
### Between (start date of intervention) and (end date of intervention), did you make any adjustments to your menu prices?
### Yes, prices were raised
### Yes, prices were lowered
### No changes were made
ggplot(data = all_simulated_dataset, mapping = aes (x = Q10, fill = type)) +
  geom_bar() +  
  coord_flip() + 
  scale_x_discrete(limit = c("Yes, prices were raised", "Yes, prices were lowered", "No changes were made")) + 
  labs(x = "Adjustments to Menu Prices",
       y = "# of Restaurants",
       title = str_wrap("Menu adjustments between Oct 1 and Dec 31", 30),
       fill = "Condition") +
  scale_fill_tableau(labels = c("Control", "Intervention"), guide = guide_legend(reverse = TRUE)) +
  theme_fivethirtyeight()

### Chi-squared test
q11_chi <- table(all_simulated_dataset$Q11, all_simulated_dataset$type) %>%
  chisq.test()
tableChisq("Pearson's Chi-squared test to examine the association of the intervention with price adjustments", q11_chi$statistic, q11_chi$parameter, q11_chi$p.value)
```

@@

```{r Q12, echo = FALSE, message = FALSE}
### Between (start date of intervention) and (end date of intervention) did you reduce your ### restaurant’s hours of operation?
### Yes
### No
ggplot(data = all_simulated_dataset, mapping = aes(x = Q12, fill = type)) +
  geom_bar(position = position_dodge(1)) +
  labs(x = "Reduction in hours of operation",
       y = "# of restaurants",
       title = str_wrap("Reducton in operating hours between Oct 1 and Dec 31", 30),
       fill = "Condition") +
  theme_fivethirtyeight() +
  scale_fill_tableau(labels = c("Control", "Intervention"), guide = guide_legend(reverse = TRUE))

### Chi-squared test
q12_chi <- table(all_simulated_dataset$Q12, all_simulated_dataset$type) %>%
  chisq.test()
tableChisq("Pearson's Chi-squared Test for Q12", q12_chi$statistic, q12_chi$parameter, q12_chi$p.value)
```

```{r Q13, echo = FALSE, message = FALSE}
### If yes, approximately how many hours per week did you reduce by
### 15% or less
### 15-30%
### 30-50%
### 50-75%
### 75% or more
ggplot(data = all_simulated_dataset, mapping = aes(x = Q13, fill = type)) +
  geom_bar(position = "stack") +
  labs(x = "Hours Reduced per Week",
       y = "# of Restaurants",
       title = str_wrap("Percentage of hours reduced between Oct 1 and Dec 31", 30),
       fill = "Condition") +
  scale_fill_tableau(labels = c("Control", "Intervention"), guide = guide_legend(reverse = TRUE)) +
  theme_fivethirtyeight()
```

```{r Q14, echo = FALSE, message = FALSE}
### Between (start date of intervention) and (end date of intervention) did you reduce the 
### number of days your restaurant was open to the public?
### Yes
### No 
ggplot(data = all_simulated_dataset, mapping = aes(x = Q14, fill = type)) +
  geom_bar(position = position_dodge(1)) +
  labs(x = "Reduction in Days of Operation",
       y = "# of Restaurants",
       title = str_wrap("Reduction of operating days between Oct 1 and Dec 31", 30),
       fill = "Condition") +
  scale_fill_tableau(labels = c("Control", "Intervention"), guide = guide_legend(reverse = TRUE)) +
  theme_fivethirtyeight()

### Chi-squared test
q14_chi <- table(all_simulated_dataset$Q14, all_simulated_dataset$type) %>%
  chisq.test()
tableChisq("Pearson's Chi-squared Test for Q14", q14_chi$statistic, q14_chi$parameter, q14_chi$p.value)
```

```{r Q15, echo = FALSE, message = FALSE}
### If yes, how many days per week did you reduce by?
### 1-2 days
### 3-4 days
### 5-6 days
### 7 days
### Not Applicable
### bar graph/pie chart/line
ggplot(data = all_simulated_dataset, mapping = aes(x = Q15, fill = type)) +
  geom_bar(position = "stack") +
  labs(x = "Days Reduced",
       y = "# of Restaurants",
       title = "Reduction in days of operation per week",
       fill = "Condition") +
    scale_fill_tableau(labels = c("Control", "Intervention"), guide = guide_legend(reverse = TRUE)) +
  theme_fivethirtyeight()
```

```{r Q16, echo = FALSE, message = FALSE}
### Have you applied for and received any external funding or grants for your restaurant since (intervention start date)?
### Yes
### No
ggplot(data = all_simulated_dataset, mapping = aes(x = Q16, fill = type)) +
  geom_bar(position = position_dodge(1)) +
  labs(x = "Application status",
       y = "# of restaurants",
       title = str_wrap("Funding Applications between Oct 1 and Dec 31", 30),
       fill = "Condition") +
  theme_fivethirtyeight() +
  scale_fill_tableau(labels = c("Control", "Intervention"), guide = guide_legend(reverse = TRUE))
```

>>>>

```{r Q7, echo = FALSE, message = FALSE, fig.cap = "The changes of revenue between Oct 1 and Dec 31"}
### Between Oct 1 and Dec 31 was your total sales revenue higher, lower, or about the same as it was during the previous quarter (last quarter dates)? *
### Higher
### Lower
### Around the Same
ggplot(data = all_simulated_dataset, mapping = aes(x = Q7, fill = type)) + 
  geom_bar() +
  labs(x = "Revenue Change",
       y = "# of Restaurants",
       title = "Revenue changes during the intervention",
       fill = "Condition") +
  theme_fivethirtyeight() + 
  scale_fill_tableau(labels = c("Control", "Intervention"), guide = guide_legend(reverse = TRUE))

```{r, echo = FALSE, message = FALSE}
### Chi-squared test
q7_chi <- table(all_simulated_dataset$Q7, all_simulated_dataset$type) %>%
  chisq.test()
tableChisq("Pearson's Chi-squared test to examine the possibility of an association between the intervention and the total sales", q7_chi$statistic, q7_chi$parameter, q7_chi$p.value)
```

```{r Q8, echo = FALSE, message = FALSE, fig.cap = "The percentage of total sales revenue decrease between Oct 1 and Dec 31"}
### What was the approximate percentage decrease in total sales revenue between Oct 1 and Dec 31 compared to the during the previous quarter (last quarter dates)? *
### Decline of 50% or more
### Decline of 25% to 50%
### Decline of 10% to 25%
### Decline of 10% or less
ggplot(data = all_simulated_dataset, mapping = aes (x = Q8, fill = type)) +
  geom_bar(position = "stack") + coord_flip() +
  scale_x_discrete(limit = c("Decline of 50% or more", "Decline of 25% to 50%", "Decline of 10% to 25%", "Decline of 10% or less")) + 
  labs(x = "Aprrox. % Decrease in Total Sales Revenue",
       y = "# of Restaurants",
       title = str_wrap("Percentage of total sales revenue decrease during the intervention", 40),
       fill = "Condition") +
  theme_fivethirtyeight() + 
  scale_fill_tableau(labels = c("Control", "Intervention"), guide = guide_legend(reverse = TRUE))

```{r, echo = FALSE, message = FALSE}
### Chi-squared test
q8_chi <- table(all_simulated_dataset$Q8, all_simulated_dataset$type) %>%
  chisq.test()
tableChisq("Pearson's Chi-squared test to examine the relation between the intervention and the total sales and a decline in revenue", q8_chi$statistic, q8_chi$parameter, q8_chi$p.value)
```

```{r Q9, echo = FALSE, message = FALSE, fig.cap = "The total revenue from takeout or delivery prior to Oct 1"}
### Before Oct 1st, approximately how much of your total monthly sales revenue came from takeout or delivery? *
### Did not offer takeout or delivery
### 25% or less
### 25- 50%
### 50-75%
### 75% or more

my_title = "Total revenue from takeout/delivery prior to the intervention"
ggplot(data = all_simulated_dataset, mapping = aes (x = Q9, fill = type)) +
  geom_bar(position = "stack") +  coord_flip() + 
  scale_x_discrete(limit = c("Did not offer takeout or delivery", "25% or less", "25-50%", "50-75%", "75% or more")) + 
  labs(x = "Total Monthly Sales Revenue Fromt Takeout or Delivery",
       y = "# of Restaurants",
       title = str_wrap("Total revenue from takeout or delivery prior to Oct 1", 30),
       fill = "Condition") +
  theme_fivethirtyeight() + 
  scale_fill_tableau(labels = c("Control", "Intervention"), guide = guide_legend(reverse = TRUE))
```

@@

```{r Q11, echo = FALSE, message = FALSE, fig.cap = "Price changes on the menu between Oct 1 and Dec 31"}
### Between (start date of intervention) and (end date of intervention), did you make any adjustments to your menu prices?
### Yes, prices were raised
### Yes, prices were lowered
### No changes were made
ggplot(data = all_simulated_dataset, mapping = aes (x = Q10, fill = type)) +
  geom_bar() +  
  coord_flip() + 
  scale_x_discrete(limit = c("Yes, prices were raised", "Yes, prices were lowered", "No changes were made")) + 
  labs(x = "Adjustments to Menu Prices",
       y = "# of Restaurants",
       title = str_wrap("Price adjustments during the intervention", 30),
       fill = "Condition") +
  scale_fill_tableau(labels = c("Control", "Intervention"), guide = guide_legend(reverse = TRUE)) +
  theme_fivethirtyeight()
```

```{r, echo = FALSE, message = FALSE}
### Chi-squared test
q11_chi <- table(all_simulated_dataset$Q11, all_simulated_dataset$type) %>%
  chisq.test()
tableChisq("Pearson's Chi-squared test to examine the association of the intervention with price adjustments", q11_chi$statistic, q11_chi$parameter, q11_chi$p.value)
```

@@

```{r Q12, echo = FALSE, message = FALSE, fig.cap = "Reduced operating hours between Oct 1 and Dec 31"}
### Between (start date of intervention) and (end date of intervention) did you reduce your ### restaurant’s hours of operation?
### Yes
### No
ggplot(data = all_simulated_dataset, mapping = aes(x = Q12, fill = type)) +
  geom_bar(position = position_dodge(1)) +
  labs(x = "Reduction in hours of operation",
       y = "# of restaurants",
       title = str_wrap("Reducton in operating hours during the intervention", 30),
       fill = "Condition") +
  theme_fivethirtyeight() +
  scale_fill_tableau(labels = c("Control", "Intervention"), guide = guide_legend(reverse = TRUE))
```

```{r, echo = FALSE, message = FALSE}
### Chi-squared test
q12_chi <- table(all_simulated_dataset$Q12, all_simulated_dataset$type) %>%
  chisq.test()
tableChisq("Pearson's Chi-squared Test for Q12", q12_chi$statistic, q12_chi$parameter, q12_chi$p.value)
```

```{r Q13, echo = FALSE, message = FALSE, fig.cap = "The percentage of operating hours reduced between Oct 1 and Dec 31"}
### If yes, approximately how many hours per week did you reduce by
### 15% or less
### 15-30%
### 30-50%
### 50-75%
### 75% or more
ggplot(data = all_simulated_dataset, mapping = aes(x = Q13, fill = type)) +
  geom_bar(position = "stack") +
  labs(x = "Hours Reduced per Week",
       y = "# of Restaurants",
       title = str_wrap("Percentage of reduced operating hours during the intervention", 30),
       fill = "Condition") +
  scale_fill_tableau(labels = c("Control", "Intervention"), guide = guide_legend(reverse = TRUE)) +
  theme_fivethirtyeight()
```

```{r Q14, echo = FALSE, message = FALSE, fig.cap = "Operating days reduced between Oct 1 and Dec 31"}
### Between (start date of intervention) and (end date of intervention) did you reduce the 
### number of days your restaurant was open to the public?
### Yes
### No 
ggplot(data = all_simulated_dataset, mapping = aes(x = Q14, fill = type)) +
  geom_bar(position = position_dodge(1)) +
  labs(x = "Reduction in Days of Operation",
       y = "# of Restaurants",
       title = str_wrap("Operating days reduced during the intervention", 30),
       fill = "Condition") +
  scale_fill_tableau(labels = c("Control", "Intervention"), guide = guide_legend(reverse = TRUE)) +
  theme_fivethirtyeight()
```

```{r, echo = FALSE, message = FALSE}
### Chi-squared test
q14_chi <- table(all_simulated_dataset$Q14, all_simulated_dataset$type) %>%
  chisq.test()
tableChisq("Pearson's Chi-squared Test for Q14", q14_chi$statistic, q14_chi$parameter, q14_chi$p.value)
```

```{r Q15, echo = FALSE, message = FALSE, fig.cap = "The percentage of operating days reduced between Oct 1 and Dec 31"}
### If yes, how many days per week did you reduce by?
### 1-2 days
### 3-4 days
### 5-6 days
### 7 days
### Not Applicable
### bar graph/pie chart/line
ggplot(data = all_simulated_dataset, mapping = aes(x = Q15, fill = type)) +
  geom_bar(position = "stack") +
  labs(x = "Days Reduced",
       y = "# of Restaurants",
       title = "Percentage of reduced operating days during the intervention",
       fill = "Condition") +
    scale_fill_tableau(labels = c("Control", "Intervention"), guide = guide_legend(reverse = TRUE)) +
  theme_fivethirtyeight()
```

```{r Q16, echo = FALSE, message = FALSE, fig.cap = "Funding applications during the intervention"}
### Have you applied for and received any external funding or grants for your restaurant since (intervention start date)?
### Yes
### No
ggplot(data = all_simulated_dataset, mapping = aes(x = Q16, fill = type)) +
  geom_bar(position = position_dodge(1)) +
  labs(x = "Application status",
       y = "# of restaurants",
       title = str_wrap("Funding applications between Oct 1 and Dec 31", 30),
       fill = "Condition") +
  theme_fivethirtyeight() +
  scale_fill_tableau(labels = c("Control", "Intervention"), guide = guide_legend(reverse = TRUE))
```
